Precision calculations for cosmic shear

### 2017-02-09 conclusions.tex
Fixed the multiple entries in the bibliography

Finally we propose that future surveys seek to optimise the statistical analyses of their cosmic shear data.  For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{schneider/etal:2010} renders the cosmic shear measurement insensitive to the low-$\ell$ scales where the Limber and flat-sky approximations make any impact on the precision of the theoretical modelling.

>>>>

Finally we propose that future surveys seek to optimise the statistical analyses of their cosmic shear data.  For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{COSEBIs} renders the cosmic shear measurement insensitive to the low-$\ell$ scales where the Limber and flat-sky approximations make any impact on the precision of the theoretical modelling.

### 2017-02-09 limber2.tex
Fixed the multiple entries in the bibliography

Most cosmic shear analysis to date have been performed on real-space
correlation statistics, since these can be measured direcaly from an observed
galaxy shape catalogue. The basic quantity is the two-point correlation
function \citep{miraldaescude:1991}, which is given by
%
\begin{eqnarray}
  \xi_+(\theta) 
  % &
  = \frac 1 {2\pi} \int {\rm d} \ell \, \ell {\rm J}_0(\ell
   \theta)
  P^\gamma(\ell);
  \quad
  %\nonumber \\
   %
   \xi_-(\theta)
  %&
  = \frac 1 {2\pi} \int
   {\rm d} \ell \, \ell {\rm J}_4(\ell \theta)
  P^\gamma(\ell).
  %
   \label{eqn:xiGG}
\end{eqnarray}
%
where ${\rm J}_\nu$ first-kind Bessel function of order $\nu$. The flat-sky
shear power spectrum $P^\gamma$ an be related to the underlying matter power
spectrum through equation \ref{eq:P_ell_limber1} when adopting a first-order
extended Limber approximation, or equation~\ref{eq:P_ell_limber2} when adopting
a second-order extended Limber approximation \citep[for more details see][and
references therein]{miraldaescude:1991, kaiser:1992,
bartelmann/schneider:2001}.

>>>>

Most cosmic shear analysis to date have been performed on real-space
correlation statistics, since these can be measured direcaly from an observed
galaxy shape catalogue. The basic quantity is the two-point correlation
function \citep{miraldaescude:1991}, which is given by
%
\begin{eqnarray}
  \xi_+(\theta) 
  % &
  = \frac 1 {2\pi} \int {\rm d} \ell \, \ell {\rm J}_0(\ell
   \theta)
  P^\gamma(\ell);
  \quad
  %\nonumber \\
   %
   \xi_-(\theta)
  %&
  = \frac 1 {2\pi} \int
   {\rm d} \ell \, \ell {\rm J}_4(\ell \theta)
  P^\gamma(\ell).
  %
   \label{eqn:xiGG}
\end{eqnarray}
%
where ${\rm J}_\nu$ first-kind Bessel function of order $\nu$. The flat-sky
shear power spectrum $P^\gamma$ an be related to the underlying matter power
spectrum through equation \ref{eq:P_ell_limber1} when adopting a first-order
extended Limber approximation, or equation~\ref{eq:P_ell_limber2} when adopting
a second-order extended Limber approximation \citep[for more details see][and
references therein]{miraldaescude:1991, kaiser:1992, BS01}.
